Constructive Preference Elicitation by Setwise Max-margin Learning

### 2016-01-28 paper/ijcai16.tex
typo

We adopt the {\em indifference-augmented} Bradley-Terry user response
model introduced in~\cite{guo2010real}. According to the classical
(without indifference) Bradley-Terry model~\cite{BraTer52}, when queried about a pair
of configurations, the probability that a user will prefer
configuration $\vx^i$ over the alternative $\vx^j$ amounts to:
%
$$ (1 + \exp(-\lambda_1 \langle\vw,\vx^i - \vx^j\rangle))^{-1} $$
%
where $\vw$ is the weight vector of the true underlying user utility.
In other words, the probability grows with the difference between the
utilities of the two items. Support for indifference has been
introduced in~\cite{guo2010real} by postulating that the probability
of the user being indifferent about the two configurations depends on
how close their utilities are, as in the exponential distribution:
%
$$ \exp(-\lambda_2 |\langle\vw,\vx^i - \vx^j\rangle|). $$
%
The parameters $\lambda_1$ and $\lambda_2$ were set to one for all
simulations\footnote{When experiment with EUS and QI, the user is forced to select
its preffered item, so indifference is not possible. While support for indifference
could be added, we chose to .}, as in~\cite{guo2010real}.

>>>>

We adopt the {\em indifference-augmented} Bradley-Terry user response
model introduced in~\cite{guo2010real}. According to the classical
(without indifference) Bradley-Terry model~\cite{BraTer52}, when queried about a pair
of configurations, the probability that a user will prefer
configuration $\vx^i$ over the alternative $\vx^j$ amounts to:
%
$$ (1 + \exp(-\lambda_1 \langle\vw,\vx^i - \vx^j\rangle))^{-1} $$
%
where $\vw$ is the weight vector of the true underlying user utility.
In other words, the probability grows with the difference between the
utilities of the two items. Support for indifference has been
introduced in~\cite{guo2010real} by postulating that the probability
of the user being indifferent about the two configurations depends on
how close their utilities are, as in the exponential distribution:
%
$$ \exp(-\lambda_2 |\langle\vw,\vx^i - \vx^j\rangle|). $$
%
The parameters $\lambda_1$ and $\lambda_2$ were set to one for all
simulations\footnote{When experimenting with EUS and QI, the user is forced to select
its preffered item, so indifference is not possible. While support for indifference
could be added, we chose to be consistent with the methods as originally published.}, as in~\cite{guo2010real}.
